\prechapter{Acknowledgements}

\begin{quote}
``{\it Results based on 12 mental health symptoms (GHQ-12) showed that 32\% of PhD students are at risk of having or developing a common psychiatric disorder, especially depression.}''

-- \citet{LEVECQUE2017868}
\end{quote}

% Pierre and Barry and Amaury
I would like to thank my primary supervisor, Pierre Maxted, for always encouraging me do science better. No Journey through research is straightforward. The journey which produced this work involved scaling many mountains, crossing many riverines and navigating the thickest fog. You patiently nudged me in the right direction to ensure I never ventured too far from the beaten track, and for that I am exceptionally grateful. I would also like to thank my second supervisor, Barry Smalley, who always had an open ear to discuss all things spectroscopy. I thank Jessica Evans, Daniel Evans, John Southworth, David Anderson and Amaury Triaud for assisting in observations which feature in this work.


% Katie and Bruce
Students in research degrees, and academia in general, face higher mental health risks than other professions. Lone working, stress and \textit{impostor syndrome} often leads to depression, guilt, isolation and negative thoughts. This often degrades ones self-confidence and the relationships with those closest to us. I would be fooling myself if I didn't acknowledge that I have experienced some, if not all of the symptoms mentioned above whilst studying for my doctorate. I would never have been able to survive my Ph.D without the endless love and support of my wife, Katie. Thank you for always bringing a smile to my face and helping me weather the harshest of storms. I  thank my parents, Jean and Simon Gill. You provided me with emotional and financial support during my research, as well as invaluable guidance. For this I am eternally grateful.

I would also like to honourably mention our beagle, Bruce McGill. Throughout my research you slept on my feet, taxed all my crunchy goods and pestered me for \textit{walkies}. Those walks provided crucial down time which helped me relax and preserved my sanity. Thank you for needing so little and doing so much. 